---
title: 'Bootstrapping C-Differences'
author: "Kenley Pelzer, Kevin Zhang"
date: "`r format(Sys.time(), '%d-%b-%y')`"
output: html_document
---


```{r setup, include=FALSE}
rm(list=ls())
setwd('C:/Users/kevinz94/Desktop/HeartDataPipeline/')
if (!require('pacman')) {install.packages('pacman')}
library(pacman)
pacman::p_load(tidyverse, Hmisc, boot)


load('./late_cohort.rds')
load('./train_with_treatments_fit.rds')
load('./train_no_treatments_fit.rds')
load('./ResultsFiles/Saved_rsf_t_object.rds')
load('./ResultsFiles/Saved_rsf_n_object.rds')
later6 <- read.csv('./later6.csv')


# C-index function for CPH bootstrapping with treatment
cph_vs_6_for_boot <- function(test_cohort,indices) {
  test_data <- test_cohort[indices, ]
  survival_predictions_cph <- predict(train_with_treatments.fit,newdata = test_data,type = 'risk')
  c_cph <- Hmisc::rcorr.cens(-survival_predictions_cph,Surv(test_data$t, test_data$died_noT))['C Index']
  c6 <- Hmisc::rcorr.cens(test_data$status6,Surv(test_data$t, test_data$died_noT))['C Index']
  cph_vs_6 <- c_cph - c6
  return(cph_vs_6)
}

# C-index function for CPH bootstrapping without treatment
cphn_vs_6_for_boot <- function(test_cohort,indices){
  test_data <- test_cohort[indices, ]
  survival_predictions_cph <- predict(train_no_treatments.fit,newdata = test_data,type = 'risk')
  c_cph <- Hmisc::rcorr.cens(-survival_predictions_cph,Surv(test_data$t, test_data$died_noT))['C Index']
  c6 <- Hmisc::rcorr.cens(test_data$status6,Surv(test_data$t, test_data$died_noT))['C Index']
  cph_vs_6 <- c_cph - c6
  return(cph_vs_6)
}

# C-index function for RSF bootstrapping with treatment
rsf_vs_6_for_boot <- function(test_cohort,indices){
  test_data <- test_cohort[indices, ]
  survival_predictions_rsf <- predict(rsf_t, newdata  =  test_data)
  c_rsf <- Hmisc::rcorr.cens(-survival_predictions_rsf$predicted,  Surv(test_data$t,test_data$died_noT))['C Index']
  c6 <- Hmisc::rcorr.cens(test_data$status6,Surv(test_data$t, test_data$died_noT))['C Index']
  rsf_vs_6 <- c_rsf - c6
  return(rsf_vs_6)
}

# C-index function for RSF bootstrapping without treatment
rsfn_vs_6_for_boot <- function(test_cohort,indices){
  test_data <- test_cohort[indices, ]
  survival_predictions_rsfn <- predict(rsf_n, newdata  =  test_data)
  c_rsfn <- Hmisc::rcorr.cens(-survival_predictions_rsfn$predicted,  Surv(test_data$t,test_data$died_noT))['C Index']
  c6 <- Hmisc::rcorr.cens(test_data$status6, Surv(test_data$t,test_data$died_noT))['C Index']
  rsfn_vs_6 <- c_rsfn - c6
  return(rsfn_vs_6)
}
```

---------

Add column with 6-status ranking to the late cohort
```{r, echo=T, warning=F, comment=NA}
for_boot <- cbind(late_cohort, status6 = later6$status6)
```

---------

## CPH with Treatment
Print output to check for match with previous c-index results
```{r, echo=T, warning=F, comment=NA}
c_cpht <- cph_vs_6_for_boot(for_boot)
print(c_cpht)
```

## First Round
```{r, echo=T, warning=F, comment=NA}
set.seed(1)
results_diff <- boot::boot(data = for_boot, statistic = cph_vs_6_for_boot, R = 1)
storing_results <- results_diff$t
```

## Looped Bootstrap
```{r, echo=T, warning=F, comment=NA}
set.seed(1)
count = 50
while (count < 1000){
  results_diff <- boot::boot(data = for_boot, statistic = cph_vs_6_for_boot, R = 50)
  storing_results <- rbind(storing_results, results_diff$t)
  print(count)
  print(mean(storing_results))
  print(sd(storing_results))
  save(storing_results, file = './ResultsFiles/Saved_cph_vs_6_boot.rds')
  count = count+50
}
```


---------


## CPH without Treatment
Print output to check for match with previous c-index results
```{r, echo=T, warning=F, comment=NA}
c_cphn <- cphn_vs_6_for_boot(for_boot)
print(c_cphn)
```

## First Round
```{r, echo=T, warning=F, comment=NA}
set.seed(1)
results_diff_n <- boot::boot(data = for_boot, statistic = cphn_vs_6_for_boot, R = 1)
storing_results_n <- results_diff_n$t
```

## Looped Bootstrap
```{r, echo=T, warning=F, comment=NA}
set.seed(1)
count = 50
while (count < 1000){
  results_diff_n <- boot(data = for_boot, statistic = cphn_vs_6_for_boot, R = 50)
  storing_results_n <- rbind(storing_results_n, results_diff_n$t)
  print(count)
  print(mean(storing_results_n))
  print(sd(storing_results_n))
  save(storing_results_n, file = './ResultsFiles/Saved_cphn_vs_6_boot.rds')
  count = count+50
}
```


---------


## RSF with Treatment
Print output to check for match with previous c-index results
```{r, echo=T, warning=F, comment=NA}
c_rsf <- rsf_vs_6_for_boot(for_boot)
print(c_rsf)
```

## First Round
```{r, echo=T, warning=F, comment=NA}
set.seed(1)
results_diff <- boot::boot(data = for_boot, statistic = rsf_vs_6_for_boot, R = 1)
storing_results_r <- results_diff$t
```

## Looped Bootstrap
```{r, echo=T, warning=F, comment=NA}
set.seed(1)
count = 10
while (count < 1000){
  results_diff <- boot::boot(data = for_boot, statistic = rsf_vs_6_for_boot, R = 10)
  storing_results_r <- rbind(storing_results_r, results_diff$t)
  print(count)
  print(mean(storing_results_r))
  print(sd(storing_results_r))
  save(storing_results_r, file = './ResultsFiles/Saved_rsft_vs_6_boot.rds')
  count = count+10
}
  
```


---------


## RSF without Treatment
Print output to check for match with previous c-index results
```{r, echo=T, warning=F, comment=NA}
c_rsfn <- rsfn_vs_6_for_boot(for_boot)
print(c_rsfn)
```

## First Round
```{r, echo=T, warning=F, comment=NA}
set.seed(1)
results_diff <- boot::boot(data = for_boot, statistic = rsfn_vs_6_for_boot, R = 1)
storing_results_rn <- results_diff$t
```

## Looped Bootstrap
```{r, echo=T, warning=F, comment=NA}
set.seed(1)
count = 10
while (count < 1000){
  results_diff <- boot::boot(data = for_boot, statistic = rsfn_vs_6_for_boot, R = 10)
  storing_results_rn <- base::rbind(storing_results_rn, results_diff$t)
  print(count)
  print(mean(storing_results_rn))
  print(sd(storing_results_rn))
  save(storing_results_rn, file = './ResultsFiles/Saved_rsfn_vs_6_boot.rds')
  count = count+10
}
  
```


---------


## Calculating Differences
### P-Values
```{r, echo=T, warning=F, comment=NA}
load('./ResultsFiles/Saved_cph_vs_6_boot.rds')
cph_diff <- storing_results
load('./ResultsFiles/Saved_cphn_vs_6_boot.rds')
cphn_diff <- storing_results_n
load('./ResultsFiles/Saved_rsft_vs_6_boot.rds')
rsf_diff <- storing_results_r
load('./ResultsFiles/Saved_rsfn_vs_6_boot.rds')
rsfn_diff <- storing_results_rn


# Calculate Z-scores
cpht_diff_Z <- c_cpht / sd(cph_diff)
cphn_diff_Z <- c_cphn / sd(cphn_diff)
rsft_diff_Z <- c_rsf / sd(rsf_diff)
rsfn_diff_Z <- c_rsfn / sd(rsfn_diff)

# Calculate p-values
p_cpht <- 2 * pnorm(q = cpht_diff_Z, lower.tail = F)
print('CPHT')
print(p_cpht)

p_cphn <- 2 * pnorm(q = cphn_diff_Z, lower.tail = F)
print('CPHN')
print(p_cphn)

p_rsft <- 2 * pnorm(q = rsft_diff_Z, lower.tail = F)
print('RSFT')
print(p_rsft)

p_rsfn <- 2 * pnorm(q = rsfn_diff_Z, lower.tail = F)
print('RSFN')
print(p_rsfn)
```


### CPH, With Treatment versus 6-status
```{r, echo=T, warning=F, comment=NA}
survival_predictions_cph <- predict(train_with_treatments.fit, newdata = late_cohort, type = 'risk')
print(Hmisc::rcorrp.cens(-survival_predictions_cph, later6$status6,
                         Surv(late_cohort$t,late_cohort$died_noT), method = 2))
```

### RSF, With Treatment versus 6-status
```{r, echo=T, warning=F, comment=NA}
print(Hmisc::rcorrp.cens(-survival_predictions_t$predicted, later6$status6,
                         Surv(late_cohort$t,late_cohort$died_noT), method = 2))
```

### CPH, No Treatment versus 6-status
```{r, echo=T, warning=F, comment=NA}
survival_predictions_cphn <- predict(train_no_treatments.fit, newdata = late_cohort, type = 'risk')
print(Hmisc::rcorrp.cens(-survival_predictions_cphn, later6$status6,
                         Surv(late_cohort$t,late_cohort$died_noT), method = 2))
```

### RSF, No Treatment versus 6-status
```{r, echo=T, warning=F, comment=NA}
survival_predictions_n <- predict(rsf_n, newdata  = late_cohort, seed = -1)
print(Hmisc::rcorrp.cens(-survival_predictions_n$predicted, later6$status6,
                         Surv(late_cohort$t,late_cohort$died_noT), method = 2))
```
